Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
edits in new LT

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing the
User into Building Sustainable Software for Science}}

>>>>

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing the
User into Building Sustainable Software for Science}}
Dan Gunter's main question was, "What is needed to develop sustainable software?".
Beyond the usual suspects of funding, great developers, good
design, and software engineering practices, however, Dan placed the
users. He explained this using a traditional software development model starting
from gathering requirements, and reaching release through a design and
development and testing phase. The main deficiency that with this approach was
pointed out to be the too-late interaction with users. Instead, an alternative
approach was proposed that, at first, skips the development phase and repeatedly
goes through requirement gathering, design and user interaction/learning
phases, and only eventually starts development once an agreement is reached,
leading to an increased user satisfaction, higher adoption, and eventually to
sustained software.
